Assessing the Replicability of Psychological Science Through Pedagogy

### 2016-09-08 paper/paper.Rmd
finished ms pass

Students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to the distribution of student interest. Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general. This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students. A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.

Students chose findings from a wide variety of domains for replication. One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015]. Details of individual replications are available in SOM.

@@

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. Three replications deviated from these two criteria.  In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.  In another, we reduced the number of trials as part of the adaptation to Mechanical Turk. In the last case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).

@@

Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices. Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g. statistical tests, figures). This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by transferring results between analysis outputs and manuscripts.

@@

In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH). Each student collected two pilot samples and review was coordinated with these. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being logged by the experiment script and that analytic scripts for the confirmatory analyses functioned appropriately. After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script (acting as a participant), analytic code, and resulting output.

Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from Mechanical Turk. The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment. (All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing text). At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses. The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.

@@

Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies. Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution. Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.

@@

Of the 15 students in the class, all completed projects (two with extensions going beyond the class period), one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product. (In one case, a student did not complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review.  Thus, this project remains included.)

Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`). Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results.

@@

\begin{table}[ht]
\centering
\begin{tabular}{rl|ccccccc}
  \hline
\multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
  \hline
   &  & No & Yes & Yes & No & No & Some & Yes \\ 
  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
  \hline
  Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\
   \hline
\end{tabular}
\caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest. High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}
\end{table}

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{llrrr|r} -->
<!--   \hline -->
<!-- Mediator & Value & No & Partial & Full & Total\\  -->
<!--   \hline -->
<!-- Replicated? &  &   2 &   6 &   3 & 11 \\  -->
<!-- \hline -->
<!--   Original on turk & Yes &   1 &   2 &   2 & 5 \\  -->
<!--    & No &   1 &   4 &   1 & 6\\  -->
<!-- \hline -->
<!--   High fidelity replication? & Yes &   2 &   3 &   1  & 6\\  -->
<!--    & No &  &   3 &   2 & 5\\  -->
<!-- \hline -->
<!--   Open materials? & Yes &   1 &   3 &   1  & 4\\  -->
<!--    & Some &  &   1 &   1 & 2\\  -->
<!--    &  No &   1 &   2 &   1 & 4\\  -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \caption{\label{tab:results} Counts of instructor team replication ratings, split by various different mediating variables.} -->
<!-- \end{table} -->

@@

The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest. Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%).
There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

@@

These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility. To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom. Other formulas are given in @osc2015, Supplemental Information.]. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).

@@

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default  test suggested by @rouder2009 and did not attempt to correct for publication bias. This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments as well. Finally, we note that the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g. BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.

@@

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (d)") + 
  ylab("Rep. effect size (d)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subjective rep. rating")

@@

In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*. We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal. Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were underwhelming and further suggests the need for more replication attempts as a means for cumulative scientific progress. The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.

Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project. While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources. Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants. Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on funding for samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.

Our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate?

@@

Indeed, by the standards of clinical trials research, nearly every study we replicated in this report would be classified as exploratory research. No protocol was pre-registered, and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.  Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications. And in many cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf. @bakeman2005]. This set of features -- which, in our experience, are endemic to published psychological work -- makes replication research within the conventional statistical paradigm extremely challenging.

In our view, two recommendations will improve this situation dramatically. First, pre-registration typically requires the selection of one or a small number of statistical analyses to be designated as critical for interpretation. Were this information available, it would have simplified the problem of selecting effects to replicate in several cases. Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here, in a number of ways. In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data and analytic code is often critical for other investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is a way of allowing more flexible reuse.

>>>>

Students selected projects based on interest, rather than via a systematic sampling strategy. After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility. The modal study chosen was the first, but several students chose later studies in a set as well.  Thus, all interpretation of our findings should be with respect to this non-probability sample.  This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.

A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}. Students chose findings from a wide variety of domains for replication. One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015]. A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015]. Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015]. Details of individual replications are available in SOM.

@@

We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies. We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] 
In 
`r sum(project_plan$power_standard == "80% power")`
cases, we powered the replication attempt to 80\% post-hoc power. In 
`r sum(project_plan$power_standard == "Original")` 
cases, we used the original sample size. Three replications deviated from these two criteria.  In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.  In another, we reduced the number of trials as part of the adaptation to Mechanical Turk. In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage (details available in SOM).

@@

Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables. This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices. Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g., statistical tests and figures). This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.

@@

In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH). Each student collected two pilot samples and review was coordinated with these. The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students). The goal of this pilot was to ensure that all needed data were being logged by the experiment software and that analytic scripts for the confirmatory analyses functioned appropriately. After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script, analytic code, and resulting output.

Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from Mechanical Turk. The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment. (All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing). At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses. The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.

@@

Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study. Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications. Thus, we interpret "key statistical test" results with caution. Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.

@@

Of the 15 students in the class, all completed projects (two with extensions going beyond the class period), one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications. Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product. (In one case, a student did not complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review. We included this project in the final analysis.)

Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies. Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`). Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have an effect on the results.

@@

<!-- \begin{table}[ht] -->
<!-- \centering -->
<!-- \begin{tabular}{rl|ccccccc} -->
<!--   \hline -->
<!-- \multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\ -->
<!--   \hline -->
<!--    &  & No & Yes & Yes & No & No & Some & Yes \\  -->
<!--   Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\  -->
<!--   Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\  -->
<!--   No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\  -->
<!--   \hline -->
<!--   Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\ -->
<!--    \hline -->
<!-- \end{tabular} -->
<!-- \caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest. High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).} -->
<!-- \end{table} -->

@@

Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons). Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
vs. 
`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%). This result is consistent with a reanalysis of @osc2015 that found identified variability across contexts as a potential factor mediating replication success [@vanbavel2016; cf. @inbar2016].
There were also small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs. `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.

@@

These additional measures therefore give another sense in which replications can be successful: If we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we should increase our confidence in the effect's replicability. To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom. Other formulae are given in @osc2015, Supplemental Information.]. We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).

@@

Next, following @etz2016, we compared Bayes Factors between the original and replication. We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[A default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings. First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals. Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments. Finally, the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g. BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.

@@

p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
  geom_point(alpha = .8, 
             aes(color=replicated_TA_factor, size = collected_n)) +
  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
  scale_x_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  scale_y_continuous(limits = c(0, 1), 
                breaks = c(.1, .3, .5, .7, .9)) +
  geom_abline(slope = 1, intercept = 0, linetype = 2) +
  geom_smooth(method = "lm", se=FALSE) +
  xlab("Orig. effect size (r)") + 
  ylab("Rep. effect size (r)") + 
  theme_bw(base_size=10) + theme(legend.position="bottom") + 
  scale_size(name = "Rep. N") +
  # scale_color_solarized(guide = FALSE)
  scale_color_solarized(name = "Subjective rep. rating")

@@

In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*. We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal. Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project.

Pedagogically, we view our findings as a success. Within relatively stringent constraints, our group was able to produce a set of high-quality projects. Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants as the originals. Thus, our work here shows what is possible for motivated students using freely-available tools and resources. Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].

Scientifically, however, our results were underwhelming. Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication. These partial replications often were cases in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original. We invite readers to browse the narrative descriptions of individual replication attempts in our SOM for an object lesson in the ways that patterns of experimental findings can differ from one another beyond the significance of a single test.

Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen. In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests. Despite these limitations, the replication rate in our study was roughly consistent with previous studies [@osc2015]. In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015]. What are the causes of this relatively low rate?

@@

Indeed, by the standards of clinical trials research, nearly every study we replicated in this report would be classified as exploratory research. No protocol was pre-registered, and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.  Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications. And in some cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf. @bakeman2005]. This set of features -- which, in our experience, are endemic to published psychological work, including our own -- makes replication research within the conventional statistical paradigm extremely challenging. 
In our view, two recommendations will improve this situation dramatically. First, pre-registration typically requires the selection of one or a small number of statistical analyses to be designated as critical for interpretation. Were this information available, it would have simplified the problem of selecting effects to replicate in several cases. Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here. In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.
